A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Move case study to usage patterns

Here we categorize evals in some common groups

@@

\section{Case studies}

\begin{itemize}
\item Escape Hatch: \c{eval(unlock_binding ... )} to prevent R CMD check
  warnings
  \subsubsection{Evaluation using Data Fields} A common use of \eval is to
  evaluate expressions that access data frame columns or list (heterogeneous
  vectors) elements by name. Core R provides two functions, \c{with} and
  \c{within} that implement this pattern. These functions construct a temporary
  environment with data frame columns or list elements as the bindings.
  Side-effects performed by the evaluated expression take place in this temporary
  environment and are ignored by the \c{with} function. The \c{within} function
  copies these modifications to a local copy of the input data and returns it.
  This pattern is used quite often for statistical modeling. The modeling
  expressions is constructed from variable names whose values are supplied by a
  data frame or list.

\item Assembling call strings from components passed by callers: eval(substitute(f(x, y, z)))
\item Convenience: 
\item Dynamic code loading: \c{eval(parse(...))}. The textual input in parse can come from three places: a string, a file or in interactive R sessions directly from user input. Next to \c{parse}, there are also \c{str2expression} and \c{str2lang} which are a specialized versions of parse that do not keep source references and thus are a bit faster.
\item bypassing R CMD check in the case one accesses dangerous functions such as unlockBinding or private symbols.
\item evaling recorded calls in model-fitting functions or passing most of the current call to another function. Both ``patterns'' use the \c{match.call} to capture current call. The latter is just for laziness as it is the same as calling the new function with explicitly selecting the arguments.
\end{itemize}

>>>>

  \subsubsection{Evaluation using Data Fields} A common use of \eval is to
  evaluate expressions that access data frame columns or list (heterogeneous
  vectors) elements by name. Core R provides two functions, \c{with} and
  \c{within} that implement this pattern. These functions construct a temporary
  environment with data frame columns or list elements as the bindings.
  Side-effects performed by the evaluated expression take place in this temporary
  environment and are ignored by the \c{with} function. The \c{within} function
  copies these modifications to a local copy of the input data and returns it.
  This pattern is used quite often for statistical modeling. The modeling
  expressions is constructed from variable names whose values are supplied by a
  data frame or list.

  \subsubsection{Metaprogramming} \eval in combination with \substitute is used
  to
  Assembling call strings from components passed by callers: eval(substitute(f(x, y, z)))

  \subsubsection{Escape Hatch}: \c{eval(unlock_binding ... )} to prevent R CMD check
  warnings

  bypassing R CMD check in the case one accesses dangerous functions such as unlockBinding or private symbols.
 evaling recorded calls in model-fitting functions or passing most of the current call to another function. Both ``patterns'' use the \c{match.call} to capture current call. The latter is just for laziness as it is the same as calling the new function with explicitly selecting the arguments.

@@
